---
title: "Final Project Pitch"
author: "D.A. Kelome"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Objective of the App.  
We use the dataset *iris* from the base R package and extract the columns named *Sepal.Length*, *Sepal.Width* and *Species*.  
For reference the summaries of the three variables are displayed below;
```{r,echo=FALSE,warning=FALSE,message=FALSE}
summary(iris[,c(1,2,5)])
```
The goal of the app will be to give a prediction of *Sepal.width* given a value of *Sepal.Length* and *Species* using linear regression models by species. The app is equipped with a selection menu allowing to first read the short documentation and then proceed to using the app.

 

## Configuration of the App


- **Input Side Panel**  
it contains check boxes to select the species, and an entry box for the value of *Sepal.Length* which will be used for the prediction(s).
- **Output Panel**  
The output panel has two components:
- The upper part is a plot panel displaying the scatterplot, fitted regressions lines for the selected species (a snapshot, when all the three species are selected is given on the next slide).  
- The lower part gives the predicted value(s) of *Sepal.Width* along with the prediction margin of error corresponding to a level .95. 

## The graphics on The app.
```{r echo=FALSE,message=FALSE,warning=FALSE}
library(tidyverse)
library(ggplot2)
library(plotly)
library(patchwork)
#d=iris[,c(1,2,5)]
model_setos=lm(Sepal.Width~Sepal.Length,data=subset(iris,
                                                      iris$Species=="setosa"))
  model_virgi=lm(Sepal.Width~Sepal.Length,data=subset(iris,
                                                      iris$Species=="virginica"))
  model_versi=lm(Sepal.Width~Sepal.Length,data=subset(iris,
                                                      iris$Species=="versicolor"))
  
 plot(iris$Sepal.Length, iris$Sepal.Width, xlab = "Sepal Length", 
       ylab = "Sepal Width", type = 'n', xlim = c(3, 9), ylim = c(1, 7))
  points(iris$Sepal.Length[iris$Species=="setosa"],iris$Sepal.Width[iris$Species=="setosa"],col="red",pch=15)
  points(iris$Sepal.Length[iris$Species=="versicolor"],iris$Sepal.Width[iris$Species=="versicolor"],col="blue",pch=16)
  points(iris$Sepal.Length[iris$Species=="virginica"],iris$Sepal.Width[iris$Species=="virginica"],col="green",pch=17)
    abline(model_setos, col = "red", lwd = 2)
    abline(model_versi , col = "blue", lwd = 2)
    abline(model_virgi , col = "green", lwd = 2)
  legend( 3, 6, c("Setosa", "Versicolor","Virginica"), pch = 19, 
         col = c("red", "blue","green"), bty = "n", cex = 1.2)

```

## An example of Computation performed by the App
 
Assuming that the species is Setosa and the input value for *Sepal.Length* is 5.2,   
  
    
    
- The predicted value for *sepal.Width* will be `r round(predict(model_setos, newdata = data.frame(Sepal.Length =5.2)),3)`  
   
   
- The corresponding margin of error at level .95 will be `r round(predict.lm(model_setos, newdata = data.frame(Sepal.Length =5.2),se.fit=TRUE,level=0.95)$se.fit,3)`

